The function--sheaf dictionary for smooth commutative group schemes over finite fields, with applications over local fields

### 2014-08-20 dictionary.tex
Moved some prose to the beginning of Applications

Let $R$ be a complete discrete valuation ring $R$ with residue field $\Fq$.
Write $\m$ for the maximal ideal of $R$ and $K$ for the quotient field for $R$.
Set $S = \Spec{R}$.
For every non-negative integer $n$, set $R_n = R/\m^{n+1}$ and $S_n = \Spec{R_n}$;  
note that $S_0 = \Spec{\Fq}$ is the special fibre of $S$.

@@

@@

Suppose $X_K$ is a connected commutative algebraic group over $K$ that admits a Néron model $X$ over $R$.
%
A {\it quasicharacter of $X_K(K)$} is a group homomorphism $X_K(K) \to \EEx$ that factors through $X_K(X) = X(R)\to X(R_n)$, for some $n\in\NN_0$;
the group of quasicharacters of $X_K(K)$ will be denoted by $\Hom_\text{qc}(X_K(K),\EEx)$ and the subgroup of those that factor through $X(R_n)$ will be denoted by $\Hom_n(X_K(K),\EEx)$.
%
In this section we explain how to geometrize and categorify quasicharacters of $X_K(K)$ using quasicharacter sheaves.

@@

\begin{proof}
To begin, fix $n\in \NN$.
The following statements follow directly from Theorems~\ref{thm:snake} and \ref{thm:autornaught} together with our observations about the component group of $\Gr^R_n(X)$.
\begin{enumerate}
\item[(1)] There is a canonical short exact sequence of abelian groups 
\[
0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Frob{}} \to \QCiso{\Gr^R_n(X)} \to \Hom(X(R_n),\EEx) \to 0.
\] 
\item[(2)] For all quasicharacter sheaves $\qcs{L}$, $\qcs{L}'$ on $\Gr^R_n(X)$ and for every $\rho \in \Hom(\qcs{L},\qcs{L}')$, either $\rho$ is trivial or $\rho$ is an isomorphism.
\item[(3)] For all quasicharacter sheaves $\qcs{L}$ on $\Gr^R_n(X)$,
\[
\Aut(\qcs{L}) \iso \Hom((\pi_0(X)_{\Fq})_{\Weil{}},\EEx),
\]
canonically.
\end{enumerate}
So Theorem~\ref{thm:QCX} now follows from the fact that each $\QC(\Gr^R_n(X))$ is a full subcategory of $\QC(\Gr_R(X))$ and the observation that $\QC(\Gr_R(X))$ a `union' of the subcategories $\QC(\Gr^R_n(X))$ in $\mathcal{C}(\Gr_R(X))$.
\end{proof}

>>>>

Let $R$ be a complete discrete valuation ring $R$ with residue field $\Fq$.
Write $\m$ for the maximal ideal of $R$ and $K$ for the quotient field for $R$.
For every non-negative integer $n$,  set $R_n = R/\m^{n+1}$.

Suppose $X_K$ is a connected commutative algebraic group over $K$ that admits a Néron model $X$ over $R$.
%
A {\it quasicharacter of $X_K(K)$} is a group homomorphism $X_K(K) \to \EEx$ that factors through $X_K(X) \to X(R_n)$, for some $n\in\NN_0$;
the group of quasicharacters of $X_K(K)$ will be denoted by $\Hom_\text{qc}(X_K(K),\EEx)$ and the subgroup of those that factor through $X(R_n)$ will be denoted by $\Hom_n(X_K(K),\EEx)$.
%
In this section we explain how to geometrize and categorify quasicharacters of $X_K(K)$ using quasicharacter sheaves.

@@

Let $K$, $R$ and $R_n$ be as above.
Set $S = \Spec{R}$.
For every non-negative integer $n$,  and $S_n = \Spec{R_n}$;  
note that $S_0 = \Spec{\Fq}$ is the special fibre of $S$.

@@

@@

\begin{proof}
To begin, fix $n\in \NN$.
The following statements follow directly from Theorems~\ref{thm:snake} and \ref{thm:autornaught} together with our observations about the component group of $\Gr^R_n(X)$.
\begin{enumerate}
\item[(1)] There is a canonical short exact sequence of abelian groups 
\[
0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Frob{}} \to \QCiso{\Gr^R_n(X)} \to \Hom(X(R_n),\EEx) \to 0.
\] 
\item[(2)] For all quasicharacter sheaves $\qcs{L}$, $\qcs{L}'$ on $\Gr^R_n(X)$ and for every $\rho \in \Hom(\qcs{L},\qcs{L}')$, either $\rho$ is trivial or $\rho$ is an isomorphism.
\item[(3)] For all quasicharacter sheaves $\qcs{L}$ on $\Gr^R_n(X)$,
\[
\Aut(\qcs{L}) \iso \Hom((\pi_0(X)_{\Fq})_{\Weil{}},\EEx),
\]
canonically.
\end{enumerate}
So Theorem~\ref{thm:QCXK} now follows from the fact that each $\QC(\Gr^R_n(X))$ is a full subcategory of $\QC(\Gr_R(X))$ and the observation that $\QC(\Gr_R(X))$ a `union' of the subcategories $\QC(\Gr^R_n(X))$ in $\mathcal{C}(\Gr_R(X))$.
\end{proof}
